Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex
small step
small-step case

\redrule{
\sOOreturn{v_1}{(\kOOconsI{\rho}{e_2}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}

@@

\redrule{
\sOOreturn{v_1}{(\kOOappI{\rho}{e_2}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}

@@

\redrule{
\sOOreturn{v_1}{(\kOOcaseI{\rho}{e_2}{e_3}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOcaseII{E}{v_1}{e_3}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOcaseII{\rho}{v_1}{e_3}{\kappa})}}{
\sOOinspect{e_3}{\rho}{
	(\kOOcaseIII{v_1}{v_2}{\kappa})
}}{}	
		\redrule{
		\sOOreturn{v_3}{(
			\mathtt{case_3} \;
			v_1 \; v_2 \;
			\kappa
			)}
	}{case(v_1,
		\mathtt{app_2} \; v_2 \; \kappa,
		\mathtt{app_2} \; v_3 \; \kappa
		)}{}

@@

\redrule{
\sOOhalt{o}}{
\sOOhalt{o}}{}
	\end{array}
	\]

	\fbox{$case(v, \kappa, \kappa) = s$}
	\[
	\begin{array}{rclr}
	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_1}
	}{}
	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
		\sOOreturn{v}{\kappa_2}
	}{}
	\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
		case(v,
		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
	}{}
	\end{array}
	\]

@@

The reduction relation $ \judgeCreduce{s}{s} $ depends on $ applyCast $, a 
function depending on blame strategies. We will give the definitions of $ 
applyCast $ shortly.
To evaluate a cast 
expression, the machine move the 
cast to the continuation and evaluate the inner expression. To apply a casted 
function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
operand to $ v_2 $, the un-casted function, and finally cast the result of the 
function application. To take out the first (resp. second) part of a casted 
pair, the machine firstly take out the first (resp. second) part of $ v $, the 
un-casted pair, and cast the result. To case-split a sum, the machine looks 
deep inside the value to find out whether it is a left injection or a right 
one.
\todo[inline]{Change the rules for case to be small step, i.e.,
	the case function should not be recursive. -JS}
Along the way, the machine accumulates the pending casts onto the 
continuations. To cast a value, the machine try to apply the cast to the value. 
If the cast succeeds, the machine returns the result to the next continuation. 
If the cast fails, the machine halts with the blame label.

>>>>

\redrule{
\sOOreturn{v_1}{(\kOOconsI{e_2}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOconsII{v_1}{\kappa})}}{}

@@

\redrule{
\sOOreturn{v_1}{(\kOOappI{e_2}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOappII{v_1}{\kappa})}}{}

@@

\redrule{
\sOOreturn{v_1}{(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{
\sOOinspect{e_2}{\rho}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{}

\redrule{
\sOOreturn{v_2}{(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})}}{
\sOOinspect{e_3}{\rho}{
	(\kOOcaseIII{v_1}{v_2}{\kappa})
}}{}

\redrule{
\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinl{v})\;v_2\;\kappa)}
}{
\sOOreturn{v}{(\kOOappII{v_2}{\kappa})}
}{}

\redrule{
	\sOOreturn{v_3}{(\mathtt{case_3}\;(\vOOinr{v})\;v_2\;\kappa)}
}{
\sOOreturn{v}{(\kOOappII{v_3}{\kappa})}
}{}

\redrule{
	\sOOreturn{v_3}{(\mathtt{case_3}\;
		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
		\;v_2\;\kappa)}
}{
	\sOOreturn{v_3'}{
		(\mathtt{case_3}\;v
		\;v_2'\;\kappa)
	}
}{\\&&
\text{where}\;
v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}
\\&&
\text{and}\;
v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}
}

@@

\redrule{
\sOOhalt{o}}{
\sOOhalt{o}}{}
	\end{array}
	\]	
%	
%	\fbox{$case(v, \kappa, \kappa) = s$}
%	\[
%	\begin{array}{rclr}
%	\funrule{case(\vOOinl{v},\kappa_1,\kappa_2)}{
%		\sOOreturn{v}{\kappa_1}
%	}{}
%	\funrule{case(\vOOinr{v},\kappa_1,\kappa_2)}{
%		\sOOreturn{v}{\kappa_2}
%	}{}
%	
%\funrule{case(\vOOcast{v}{\cOOcast{\POOsum{T_{11}}{T_{12}}}{l}{\POOsum{T_{21}}{T_{22}}}},\kappa_1,\kappa_2)}{
%		case(v,
%		\langle \cOOcast{T_{11}}{l}{T_{21}} \rangle \kappa_1,
%		\langle \cOOcast{T_{12}}{l}{T_{22}} \rangle \kappa_2)
%	}{}
%	\end{array}
%	\]

@@

The reduction relation $ \judgeCreduce{s}{s} $ depends on $ applyCast $, a 
function depending on blame strategies. We will give the definitions of $ 
applyCast $ shortly.
To evaluate a cast 
expression, the machine move the 
cast to the continuation and evaluate the inner expression. To apply a casted 
function, the machine firstly cast $ v_1 $, the operand, then apply the casted 
operand to $ v_2 $, the un-casted function, and finally cast the result of the 
function application. To take out the first (resp. second) part of a casted 
pair, the machine firstly take out the first (resp. second) part of $ v $, the 
un-casted pair, and cast the result. In case spliting, if the target value is a 
left injection, the machine moves to a state that will apply the first 
continuation function to the value inside the left injection. The case for 
right injection is similar. When the target value is a casted sum, the machine 
moves the cast from the target value to continuations functions. 
\todo[inline]{Change the rules for case to be small step, i.e.,
	the case function should not be recursive. -JS
\\---\\ Fixed. -KC}
%Along the way, the machine accumulates the pending casts onto the 
%continuations. 
To cast a value, the machine try to apply the cast to the value. 
If the cast succeeds, the machine returns the result to the next continuation. 
If the cast fails, the machine halts with the blame label.
When the continuation is $ stop $, the machine enters a halting state. The 
When the machine is in a halting state, it stays in the same state.
